---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# qmactools

<!-- badges: start -->
<!-- badges: end -->

The goal of qmactools is to provide a set of bash scripts that helps in the installation of certain programs.

## Installation

You can install the released version of qmactools from GitHub

```
git clone https://github.com/fbzwsqualitasag/qmactools.git
```

## Examples

After the download you can install the latest version of R using 

```
cd qmactools/bash
./qmac_installr.sh
```

The RStudio IDE can be installed running the bash script

```
./qmac_installrstudio.sh
```

The office suite LibreOffice can be installed running the following script

```
./qmac_installlibo.sh
```

```{r, echo=FALSE, results='asis'}
cat(paste0(c("\n---\n\n _Latest Changes: ", format(Sys.time(), "%Y-%m-%d %H:%M:%S"), " (", Sys.info()[["user"]], ")_"), collapse = ''), "\n")
```




